### 2016-03-19 config/glossaries.inc.tex
Import LRM Hinf files
Atually include figures + text from CH04
Some musings in future research
Import LRM-paper draft

\newacronym{ADC}{ADC}{analog-to-digital converter}

@@

\newacronym{ETFE}{ETFE}{empirical transfer function estimate}

@@

\newacronym{LML}{LML}{log marginal likelihood}
\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}

@@

\newacronym{PDF}{PDF}{probability distribution function}
\newacronym{PSD}{PSD}{power spectral density}

\newacronym{RAM}{RAM}{random-access memory}
\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}

\newacronym{SIMO}{SIMO}{single-input multiple-output}
\newacronym{SISO}{SISO}{single-input single-output}
\newacronym{SPICE}{SPICE}{Simulation Program with Integrated Circuit Emphasis}
\newacronym{SNR}{SNR}{signal to noise ratio}

>>>>

\newacronym{ADC}{ADC}{analog-to-digital converter}
\newacronym{AICc}{AICc}{Akaike's information criterion corrected for small sample sizes}
\newacronym{AIC}{AIC}{Akaike's information criterion}
\newacronym{AVIS}{AVIS}{active vibration isolation system}

@@

\newacronym{EIV}{EIV}{errors-in-variables}
\newacronym{ETFE}{ETFE}{empirical transfer function estimate}

@@

\newacronym{LCF}{LCF}{left co-prime factorization}
\newacronym{LFT}{LFT}{linear fractional transformation}
\newacronym{LML}{LML}{log marginal likelihood}
\newacronym{LOOCV}{LOOCV}{leave-one-out cross-validation}
\newacronym{LMM}{LMM}{Local Modeling Method}
\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LPV}{LPV}{linear parameter-varying}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}
\newacronym{LTV}{LTV}{linear time-varying}

@@

\newacronym{PDF}{PDF}{probability distribution function}
\newacronym{PRESS}{PRESS}{prediction residual error sum of squares}
\newacronym{PSD}{PSD}{power spectral density}

\newacronym{RAM}{RAM}{random-access memory}
\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
\newacronym{RCF}{RCF}{right co-prime factorization}
\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}

\newacronym{SA}{SA}{spectral analysis}
\newacronym{SIMO}{SIMO}{single-input multiple-output}
\newacronym{SISO}{SISO}{single-input single-output}
\newacronym{SPICE}{SPICE}{Simulation Program with Integrated Circuit Emphasis}
\newacronym{SNR}{SNR}{signal to noise ratio}
\newacronym{STFT}{STFT}{short-time Fourier transform}
